Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-10-13 methods_paper/fabl-paper.tex
suggestions to abstract.

In this paper, we propose the \emph{fast beta linkage} method (\texttt{fabl}), which extends a recent Bayesian Fellegi Sunter model for increased efficiency and scalability. Specifically, we relax the one-to-one matching requirement of the Beta Record Linkage method of \citep{sadinle_bayesian_2017} and propose independent priors over the matching space. This allows us to employ hashing techniques that hasten calculations and reduce the overall computational complexity. In addition, we are able to complete pairwise record comparisons over large datasets through parallel computing and reduce memory costs through a new technique called \emph{storage efficient indexing}. Through simulation studies and a case study of homicides from the El Salvadoran Civil War, we show that our method has markedly increased speed with minimal loss of accuracy. Finally, we discuss our work and future directions.

\end{abstract}

>>>>

In this paper, we propose the \emph{fast beta linkage} method (\texttt{fabl}), which extends a recent Bayesian Fellegi Sunter model for increased efficiency and scalability. Specifically, we relax the one-to-one matching requirement of the Beta Record Linkage method of \citep{sadinle_bayesian_2017} and propose independent priors over the matching space. \textcolor{red}{We derive the associated conditional distributions and provide a Gibbs sampling algorithm for our proposed framework.}
\textcolor{red}{Our modified prior} allows us to employ hashing techniques that hasten calculations and reduce the overall computational complexity.  In addition, we are able to complete pairwise record comparisons over large datasets through parallel computing and reduce memory costs through a new technique called \emph{storage efficient indexing}. \textcolor{red}{We derive the associated conditional distributions and provide a Gibbs sampling algorithm for our proposed framework.}
\textcolor{red}{Moreover, we provide the computational complexity of \texttt{fabl}.} Through simulation studies and a case study of homicides from the El Salvadoran Civil War, we show that our method has markedly increased speed with minimal loss of accuracy. Finally, we discuss our work and future directions. 
\end{abstract}
